Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-06-23 paper/paper.tex
12 written the conclusions better

In this study we have presented $\cplx$-valued Variational sparsification methods to
the ever growing set of tools for learning deep $\cplx$-valued neural networks. To
validate the proposed $\cplx$-valued extensions of the Variational Dropout methods
\citep{molchanov_variational_2017,kharitonov_variational_2018} we have conducted a
large numerical study of $\cplx$VNN with simple architectures to assess the feasible
performance-compression trade-off. At the cost of marginally lower performance, we have
achieved $\times50$-$\times100$ compression of the deep $\cplx$VNN of \citet{trabelsi_deep_2018}
on the MusicNet.

Analysis of experimental findings has shown that $\cplx$-VD, sec.~\ref{ssub:vd_prior},
and $\cplx$-ARD, sec.~\ref{ssub:ard_prior} offer adequate compression with controllable
performance degradation in $\cplx$VNN and have trade-off profile similar to their $\real$
counterparts.
% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
% levels of 80\% and up. Variational dropout consistently produces models on-par or better
% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
Therefore, we expect the overall conclusion of \citet{gale_state_2019} to carry over to
$\cplx$VNN, since there is nothing fundamentally different in the proposed $\cplx$-valued
variational sparsification methods.

The results of this study have direct implications for real-time signal processing with
embedded deep learning applications both in terms of lower storage requirements and higher
throughput stemming from fewer floating-point multiplications, despite higher arithmetic
complexity of $\cplx$-valued networks.
% CVNN capacity grows by \sqrt{2}, compute grows by 2 % RVNN caption by 2 compute by 2.

>>>>

In this study we have presented $\cplx$-valued variational sparsification methods to
the ever growing set of tools for learning deep $\cplx$-valued neural networks. To
validate these methods we have carried out a large numerical study of $\cplx$VNN with
simple architectures to assess the feasible performance-compression trade-off, and
studied compression of two deep convolutional $\cplx$VNN. At the cost of marginally
lower performance, we have achieved $\times50$-$\times100$ compression of the deep
$\cplx$VNN of \citet{trabelsi_deep_2018} on the MusicNet.
% CVNN capacity grows by \sqrt{2}, compute grows by 2 % RVNN caption by 2 compute by 2.

Experimental results show that $\cplx$-VD (sec.~\ref{ssub:vd_prior}) and $\cplx$-ARD
(sec.~\ref{ssub:ard_prior}) exhibit trade-off profiles matching their $\real$-valued
counterparts. This makes us confident that the overall conclusion of \citet{gale_state_2019}
is applicable to $\cplx$VNN and the proposed $\cplx$-valued variational sparsification
methods.
% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
% levels of 80\% and up. Variational dropout consistently produces models on-par or better
% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
Furthermore our findings indicate that between each other under similar circumstances
the methods yield comparable compression and performance results, which echoes earlier
results by \citet{kharitonov_variational_2018}.

The results of this study have direct implications for embedded deep learning applications
both in terms of lower storage requirements and higher throughput stemming from fewer
floating point multiplications due to sparsity, despite somewhat higher arithmetic
complexity of $\cplx$-valued networks.
